NFC and burnout in teachers - A replication and extension study

### 2021-10-26 Manuscript/Manuscript.Rmd
added column to table

  fit_table <- data.frame("Path" = c("NFC $\\rightarrow$ Self Control", "NFC $\\rightarrow$ Reappraisal", "NFC $\\rightarrow$ Suppression",
                                   "Self Control $\\rightarrow$ RPE", "Reappraisal $\\rightarrow$ RPE", "Suppression $\\rightarrow$ RPE", "NFC $\\rightarrow$ RPE",
                                   "NFC $\\rightarrow$ RPE via Self Control", "NFC $\\rightarrow$ RPE via Reappraisal", "NFC $\\rightarrow$ RPE via Suppression",
                                   "Total Effect"),
                          "Effect" = c(fit_summ$PE$est[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "SE" = c(fit_summ$PE$se[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "z-value" = c(fit_summ$PE$z[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "p-value" = c(fit_summ$PE$pvalue[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "CI Lower" = c(fit_summ$PE$ci.lower[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "CI Upper" = c(fit_summ$PE$ci.upper[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          check.names = FALSE)

@@

  replication_table <-
    kbl(fit_table,
        booktabs = T, # no vertical lines
        escape = F, # correctly print special characters)
        align = c("l",rep("r",6))) %>% # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
    pack_rows("Indirect Effects", 8, 10) %>%
    pack_rows("Total Effect", 11, 11) %>%
    footnote(general = "CI = confidence interval, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, SE = standard error.",
             escape = F, # correctly print special characters
             threeparttable = T)# line breaks in the footnote

>>>>

  fit_table <- data.frame("Path" = c("NFC $\\rightarrow$ Self Control", "NFC $\\rightarrow$ Reappraisal", "NFC $\\rightarrow$ Suppression",
                                   "Self Control $\\rightarrow$ RPE", "Reappraisal $\\rightarrow$ RPE", "Suppression $\\rightarrow$ RPE", "NFC $\\rightarrow$ RPE",
                                   "NFC $\\rightarrow$ RPE via Self Control", "NFC $\\rightarrow$ RPE via Reappraisal", "NFC $\\rightarrow$ RPE via Suppression",
                                   "Total Effect"),
                          "B" = c(fit_summ$PE$est[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "SE" = c(fit_summ$PE$se[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "z-value" = c(fit_summ$PE$z[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "p-value" = c(fit_summ$PE$pvalue[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "CI Lower" = c(fit_summ$PE$ci.lower[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "CI Upper" = c(fit_summ$PE$ci.upper[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "\beta" = c(fit_summ$PE$std.all[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          check.names = FALSE)

@@

  replication_table <-
    kbl(fit_table,
        booktabs = T, # no vertical lines
        escape = F, # correctly print special characters)
        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
    pack_rows("Indirect Effects", 8, 10) %>%
    pack_rows("Total Effect", 11, 11) %>%
    footnote(general = "B = unstandardized regression coefficient, \beta = standardized regression coefficient, CI = confidence interval, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, SE = standard error.",
             escape = F, # correctly print special characters
             threeparttable = T)# line breaks in the footnote
